---
title: "p8105_hw5_hq2163_hanbo"
author: "Hanbo Qiu"
date: "November 3, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
  )
  
library(tidyverse)
library(ggridges)
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5)))
```

##Problem 1

**Start with a dataframe containing all file names:**

```{r}
vec_names = list.files("./data", all.files = TRUE, full.names = FALSE) 

vec_names = vec_names[-1:-2]
```

**Iterate over file names, read in data for each subject, and save the result as a new variable in the dataframe**

```{r}
read_files = function(file_name) {
  
  read_csv(file = file_name）
  
}

com_names = str_c( "./data/", vec_names)

df_names = as_tibble(vec_names) %>% 
  mutate(data = map(com_names, read_files))
```

**Tidy the result; manipulate file names to include control arm and subject ID; make the observations “tidy”**

```{r}
df_names = df_names %>% 
  mutate(group = str_sub(value, 1, 3), no = 1:20) %>% 
  unnest() %>% 
  gather(key = week, value = value, week_1: week_8)
```

**Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups**

```{r}
df_names %>% 
   ggplot(aes(x = week, y = value, color = group, group = no)) +
   geom_path() + labs(
    title = "Individual observations of two groups on each subject in 8 weeks",
    x = "Week",
    y = "Individual observations",
    caption = "Data from a longitudinal study"
  ) +
  theme(legend.position = "right")
```

##Problem 2

**Describe the raw data. Create a city_state variable, summarize within cities to obtain the total number of homicides and the number of unsolved homicides**

```{r}
homicides = read_csv(file = "./homicide-data.csv") %>% 
   mutate(city_state = str_c(city, ",", state))

total_homi = homicides %>% 
   filter(disposition == "Closed without arrest") %>% 
   group_by(city) %>% 
   summarize(total_homi = n())

unsolved_homi = homicides %>% 
   filter(disposition == "Open/No arrest") %>% 
   group_by(city) %>% 
   summarize(unsolved_homi = n())
```

The raw data is collected by The Washington Post to represent a decade of homicide arrest data from 50 of the nation’s largest cities. The dataframe's dimension is `r dim(homicides)`. In each observation, we can figure out the basic information of the victim in each case of homicide. In "disposition" variable, the case was catagorized into "Closed by arrest", "Closed without arrest" and "Open/No arrest". After importing the data, we create a city_state variable to combine "city"" and "state" variable, summarize within cities to obtain the total number of homicides which is stored in the subset "total_homi" and the number of unsolved homicides in the subset "unsolved_homi".
